Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations

### 2019-02-21 paper/tidy-missing-data-paper.Rmd
just a final commit to note that this is as the paper was submitted to arxiv
add address and minor update of figures

---
title: "Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations"
author: "Nicholas Tierney, Department of Econometrics and Business Statistics, Monash University, **Corresponding author (nicholas.tierney@gmail.com)** \\newline Dianne Cook, Department of Econometrics and Business Statistics, Monash University"
date: "September 6, 2018"
toc: false
bibliography: tidy-missing-data-paper.bib
output:
  bookdown::pdf_document2:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
csl: jcgs.csl
---

>>>>

---
title: "Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations"
author: "Nicholas Tierney, Department of Econometrics and Business Statistics, Monash University, E774, Menzies Building Monash University, Clayton, 3168, Victoria, Australia **Corresponding author (nicholas.tierney@gmail.com)** \\newline Dianne Cook, Department of Econometrics and Business Statistics, Monash University"
date: "September 6, 2018"
toc: false
bibliography: tidy-missing-data-paper.bib
output:
  bookdown::pdf_document2:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
csl: jcgs.csl
---
